Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-05-15 review/response/response.tex

  \item R1.3 \textit{The authors published an initial paper on the system. With respect to that paper, here the experiments are extended, including also an analysis of the time-to-target fitting with respect to Fitts's Law.
    While the amount of novel content seems to be appropriate for a journal extension of the paper, the system description is copied verbatim from the previous paper, and Figures 1b, 2 and 3 are essentially identical. Content provided elsewhere should be summarized and readapted and not copied.}
  \item[] Thank you for pointing this out.
    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question.

  \item R1.4 \textit{The work is generally technically sound. However, there is one critical issue. The paper states: "..differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation... This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar...".
    This statement is not valid. Difference testing detects difference, but the absence of statistically significant difference does not imply similarity. For that equivalence testing is needed.}
  \item[] Thank you for pointing out this error.
    This is addressed in Section 5.3, where we confirm the statistical similarity between the 2 groups with a 2-sample Kolmogorov-Smirnov test. 
    These results are listed in Table 3.

  \item R1.5 \textit{Another important consideration that should be discussed is the high variance in the results of the participants with visual impairments. As the authors suggest, this might be an artifact due to a lower number of participants. However, there is also an alternative interpretation: prior literature on spatial understanding in people with visual impairments suggests that visual impairment onset age, prior experience with spatialized information and other characteristics impact spatial performance capabilities [millar1994understanding, pring2008psychological]. Thus, it may be that the high variance in data for visually impaired participants is due to the high variance in participants' characteristics. As the number of visually impaired participants is low, I suggest adding a table presenting participants' demographic characteristics (age, impairment, onset, navigation expertise....)}
  \item[] We thank the reviewer for this helpful suggestion.
    To address this, we added in Section 4.4 additional demographic information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
    This is summarised in Table 1.

@@

\end{itemize}

\section*{Reviewer 2}

\begin{itemize}

  \item R2.1 \textit{The authors might make mention of the Microsoft Soundscape system. While this system does not provide information about elevation, it is an example of a commercially available navigation aid that uses spatialized audio. https://www.microsoft.com/en-us/research/product/soundscape/. While I have reservations about using Fitts’s Law in this paper, probably the single best citation for the justification for using We is [zhai2004]. Also not all that critical given my reservations, but JFYI. In two-dimensional directed pointing, the calculation of We is better calculated as described in [wobbrock2011]}
  \item[] We'd like to thank the reviewer for these helpful references. 
    We have added the reference from~\cite{zhai2004speed}, as well as a paper by~\cite{kabbash1995prince}, in Section 4.3 to support our use of $w_e$ in this work.
    We have also revised the way we calculate $w_e$ based on the recommendations from the reviewer and~\cite{wobbrock2011effects} recommendations and made mention of this in Section 4.3. 
    These changes have led to modifications to Fig. 11 and 12 and have improved the overall model fit.
    The updated results are discussed in Sections 5.4 and 5.5. and listed in Table 4.

  \item R2.2 \textit{First, while it is good that the authors included visually impaired individuals in the study, it is hard to know what to make of the differences in performance (and patterns of performance) between the two groups. Since the whole point of the study is to inform a system intended to be used by visually impaired individuals, how should we interpret this? The two groups are VERY different in performance, N, and (I assume, though details are not provided) demography. While having a group of young blind-folded participants is fine as a baseline for a project like this, the apparent variability and small N in the VI group is problematic. This isn’t really a fatal flaw, but it makes the study much less robust. At a minimum, we need to know more detail about the demographic details of the two groups. Currently, the paper lumps the age range and gender together for the two groups. Because the behavior of the two groups is so different, these really need to be separated.}
  \item[] We'd like to thank the reviewer for pointing this out. 
    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table 1. 
    We have also added comments in Section 5.3 to point out that these underlying demographic differences may be the cause of the divergences between the groups.  
    Furthermore, we added an additional Kolmogorov-Smirnov test in Section 5.3 to show the statistical similarity between the groups' results, which we hope alleviates concerns about robustness.

@@

  \item R2.4 \textit{And, as seen in Fig 8, there are huge differences in the distribution of ``error'' between the two groups (G1 \& G2), and I suspect there may be even larger differences between users: different thresholds of ``good enough'' for different users. It’s also not clear to me if We is calculated for each level of Distance, or is it calculated across multiple amplitude of movements?}
  \item[] As mentioned in R2.3, the thresholds of `good enough' is this experiment's measurement.
    However, to address the reviewer's concerns and clarify our method, we have added additional details in Section 4.3 of how we determined $w_e$ and use it to determine a setting's expected performance. 
    In summary, we calculated a $w_e$ for each participant's experiment run and used the median of all the participants to fit the curves in Fig 11 and generate the $IP$ in Fig 12.

  \item R2.5 \textit{So my skepticism of the whole exercise of using Fitts’s Law for comparing these conditions is that it feels weird to me to reconstitute some form of W (We) from the spread of hits around a point target when there’s no objective feedback for hitting it (i.e., no W). Since they mostly just use this to make comparisons between different elevation stimuli, it’s not clear that they NEED to do this anyway. I think they could probably just use speed \& distance and be done with it, especially since there is no change in W. I guess if We were actually changing with different conditions (D or elevation), there might be some justification for this (though We in that case will be highly correlated with D, which would violate at least the spirit of the law), but this experiment seems way too small to detect this (and this detail isn’t reported anyway). Why go to all the trouble of doing the Fitt’s analysis when the only thing you’re varying is distance? Indeed, for the final take-aways that the authors provide, this seems like enormous overkill.}
  \item[] We'd like to thank the reviewer for this feedback.
    To address these concerns, we have added text in Section 1, where additional context behind the reason for these experiments and how their results will be used is provided. 
    In summary, for this project we were looking into ways to automate an optimisation process where an audio interface changes its own audio parameters to boost the user's target-finding performance.
    For this, we required a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
    %At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts' Law'.

  \item R2.6 \textit{I suspect that the authors want to engage in this whole Fitts’s exercise in order to tie the work more closely to the wider HCI pointing literature. However, if the authors really wanted to use Fitts’s Law for this task, there is certainly precedent in the Marentakis \& Brewster, 2006 paper that they cite. Here, researchers used a second audio signal to indicate that a target was acquired.
    All the above notwithstanding, I’m not certain that this is *wrong* for the purposes they use here, it’s just very non-standard and violates much of the basic theory behind Fitts’s Law. So I don’t see this as a completely fatal flaw, but the authors would definitely need to modify the manuscript to address these issues if they want to engage with the Fitts’s Law discourse.}
  \item[] We appreciate this feedback.
    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target position estimation error.
    However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system and we make mention of this in the concluding lines.
    Regarding Fitts's Law not being used correctly in this work, we hope that the points in R2.3-2.4 sufficiently address the reviewer's concerns.

  \item R2.7 \textit{To my mind, the paper is a bit of an ``LPU'' (least-publishable-unit), for a larger, more interesting project (which I would love to see!). The specific contribution here is in the use of a pitch gradient for conveying elevation information for spatialized 3D audio as well as a user study evaluating its effectiveness and some of the design space (three different pitch gradients). I’m not sure that I would consider this an adequate contribution for a shorter conference paper (such as ASSETS); for TACCESS, this seems weak. That is, I would say the contribution is not commensurate with the length of the paper.}
  \item[] Thank you for this helpful feedback.
    We recognise and respect the reviewer's opinion on this point.
    However, we think that the paper contains enough contributory work to justify its publication for a couple of reasons.
    Firstly, the experiments with a sizable sample of both partially-sighted blindfolded individuals provides compelling results on the expected accuracy of a modified spatialised audio signal played via bone-conduction headphones.
    Indeed, it adds to a relatively sparse body of knowledge on the matter.
    Furthermore, while not necessarily strictly proving conformance to Fitts's Law, we do show a consistent and reasonably strong fit for a non-visual search task with an audio interface with both partially-sighted and blindfolded individuals that, in our opinion, is interesting and merits publication.

### 2020-05-15 paper.tex
Updated response, added participant table, adapted figures

The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right). Adapted from~\citet{lock2019bone}.}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

@@

\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities. 
Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}

@@

\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}. 
However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
The pan angle can still be conveyed with a spatialised audio signal generated by an HRTF.
Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in~\citet{lock2019bone}.}

@@

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. Adapted from~\citet{lock2019bone}. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
This high/low scheme was selected based on humans' natural association of high-pitched sounds with elevated objects and vice-versa for low-lying objects~\citep{pratt1930spatial,blauert1997spatial}.
The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}. }

\hl{The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
This tone is heuristically set to \SI{512}{\hertz} following practical tests, which is comfortably audible for a large number of octaves changes.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.}

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception and none reported any significant prior experience with electronic navigation aids. }
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
The similarity between the distributions is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.
\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice. }

@@

This work identified a number of uncertainties that can be the focus of future work.
These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
Indeed, the work by~\citet{gallina2015progressive} may serve as a good guideline for such a system.
Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.
With this kind of audio interface now better understood, it is ready to be implemented into a fully packaged guidance system for people with visual impairments.

>>>>

The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:participant}).
This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.

\begin{figure}
  \centering
  %\subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
%~
  %\subfloat[]{\label{fig:participant}\includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}}
  \includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}
  \caption{The Tango tablet and bone-conduction headphones in use during an experiment. The angle reference system that the guidance instructions are based on is also included , showing the camera vector, $C$, and the pan and elevation angles to the target. Adapted from~\citet{lock2019bone}.}\label{fig:participant}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

@@

\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities. 
Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
The AfterShockz headphones (\cref{fig:participant}) were ultimately selected.
These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}

@@

\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:participant}).
Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}. 
However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
The pan angle can still be conveyed with a spatialised audio signal generated by an HRTF.
Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in~\citet{lock2019bone}.}

@@

\begin{figure}
  \centering
  %\subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
%~
  %\subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}
  \caption{A plot depicting the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. Adapted from~\citet{lock2019bone}. }\label{fig:pitch-gain}
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
This high/low scheme was selected based on humans' natural association of high-pitched sounds with elevated objects and vice-versa for low-lying objects~\citep{pratt1930spatial,blauert1997spatial}.
The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}. }

\hl{The pitch is changed as a linear function of the elevation angle, the gradient of which is determined by setting the angle and pitch limits.
These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
This tone is heuristically set to \SI{512}{\hertz} following practical tests, which is comfortably audible for a large number of octaves changes.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.}

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life.
Of these, 3 participants still have limited light perception with no ability to reliably discern shapes and objects. 
Nevertheless, they were asked to close their eyes during the experiment to. 
None of the participants reported any significant prior experience with electronic navigation aids and none had any hearing or other disabilities that could have influenced their performance in the experiments.
These demographics are summarised in \cref{tab:demographics}.}
Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.

\begin{table}
  \centering
  \caption{}\label{tab:demographics}
  \begin{tabular}{p{2.7cm}p{1.8cm}p{6cm}}
    \toprule
                                 & Group \textit{G1} & Group \textit{G2} \\\midrule
    Gender [M/F]                 & 10/32    & 7/3 \\
    Age [years]                  & $20\pm2$ & $61\pm17$ \\
    Degrees of Vision Impairment & N/A      & 3 totally blind, 7 severely sight impaired (3 with very limited light perception) \\
    Experience with ETAs         & None     & None \\
    \bottomrule
  \end{tabular}
\end{table}

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
The similarity between the distributions is further highlighted by a two-sample Kolmogorov-Smirnov test (the $p$-values are listed in~\cref{tab:inter-group-results}).
\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice. }

@@

This work identified a number of uncertainties that can be the focus of future work.
These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
Indeed, the work by~\citet{gallina2015progressive} may serve as a good guideline for such a system.
Additional feedback modes may also be added to allow for a clearer guidance experience for the user, e.g.\ vibration signals or another tone~\citep{marentakis2006effects}, to explicitly inform them when they are pointing to the target or by adjusting the volume to expand the system to three dimensions.
With this kind of audio interface now better understood, it is ready to be implemented into a fully implemented guidance system for people with visual impairments.
